iterSim

### 2023-04-05 analyses/optimFlchain.Rmd
rancleanedcodeCheck

preData<-data.frame(age=as.numeric(flchain$age),
                    #sampyr=as.numeric(flchain$sample.yr),
                    sex=as.factor(flchain$sex),
                    flc=as.numeric(flchain$kappa)+as.numeric(flchain$lambda),
                    #batch=as.factor(flchain$flc.grp),
                    creatine=as.numeric(flchain$creatinine),
                    mgus=as.numeric(flchain$mgus),
                    time=as.numeric(flchain$futime),
                    status=as.numeric(flchain$death)
)

@@

##saveRDS(res$test,"cvData/flchainTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
##saveRDS(klist,"cvData/flchainCV.rds")

@@

lr=c(0.01)
drpt=c(0.01)
layer1=c(50)
layer2=c(10)
nBatch=c(100)
actv=c("relu","linear")#
alp=c(0)

@@

#saveRDS(winners,"cvData/flchainWins.rds")

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  #saveRDS(BrierIPAList,'results/100flchainBrier.rds')
  #saveRDS(cScore,'results/100flchaincidx.rds')
  #saveRDS(AUClist,'results/100flchainAuc.rds')
  pos=pos+1

>>>>

preData<-data.frame(age=as.numeric(flchain$age),
                    sex=as.factor(flchain$sex),
                    flc=as.numeric(flchain$kappa)+as.numeric(flchain$lambda),
                    creatine=as.numeric(flchain$creatinine),
                    mgus=as.numeric(flchain$mgus),
                    time=as.numeric(flchain$futime),
                    status=as.numeric(flchain$death)
)

@@

saveRDS(res$test,"cvData/flchainTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"cvData/flchainCV.rds")

@@

@@

saveRDS(winners,"cvData/flchainWins.rds")

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100flchainBrier.rds')
  saveRDS(cScore,'results/100flchaincidx.rds')
  saveRDS(AUClist,'results/100flchainAuc.rds')
  pos=pos+1

### 2023-04-05 analyses/optimMyeloma.Rmd
rancleanedcodeCheck

#saveRDS(res$test,"cvData/myelomaTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
#saveRDS(klist,"cvData/myelomaCV.rds")

@@

```{r winners,eval=TRUE,hide=FALSE}
winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)
#saveRDS(winners,"cvData/myelomaWins.rds")

@@

  print(paste("current iter:",pos))
  #saveRDS(BrierIPAList,'results/100myelomaBrier.rds')
  #saveRDS(cScore,'results/100myelomacidx.rds')
  #saveRDS(AUClist,'results/100myelomaAuc.rds')
  pos=pos+1

>>>>

saveRDS(res$test,"cvData/myelomaTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"cvData/myelomaCV.rds")

@@

```{r winners,eval=TRUE,hide=FALSE}
winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)
saveRDS(winners,"cvData/myelomaWins.rds")

@@

  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100myelomaBrier.rds')
  saveRDS(cScore,'results/100myelomacidx.rds')
  saveRDS(AUClist,'results/100myelomaAuc.rds')
  pos=pos+1

### 2023-04-05 analyses/optimProstate.Rmd
rancleanedcodeCheck

#saveRDS(res$test,"cvData/prostateTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
#saveRDS(klist,"cvData/prostateCV.rds")

@@

klist<-readRDS("cvData/prostateCV.rds")

@@

#saveRDS(winners,"cvData/prostateWins.rds")

@@

  linModelTrain<-as.data.frame(rbind(train,val))
  #valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)#rbind(train,val)
  #valcb$offset<-0
  #valcbtensor<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),as.matrix(valcb[,ncol(valcb),drop=F])),as.matrix(valcb[,ncol(valcb)-1,drop=F]))
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 82
  )

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  #saveRDS(BrierIPAList,'results/100prostateBrier.rds')
  #saveRDS(cScore,'results/100prostatecidx.rds')
  #saveRDS(AUClist,'results/100prostateAuc.rds')
  pos=pos+1

>>>>

saveRDS(res$test,"cvData/prostateTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"cvData/prostateCV.rds")

@@

@@

saveRDS(winners,"cvData/prostateWins.rds")

@@

  linModelTrain<-as.data.frame(rbind(train,val))

  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 82
  )

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100prostateBrier.rds')
  saveRDS(cScore,'results/100prostatecidx.rds')
  saveRDS(AUClist,'results/100prostateAuc.rds')
  pos=pos+1

### 2023-04-05 analyses/optimizeComplex.Rmd
rancleanedcodeCheck

res = split(data, g)
#saveRDS(res$test,"cvData/ComplexSimTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
#saveRDS(klist,"cvData/ComplexSimCV.rds")

@@

```{r,eval=TRUE,hide=FALSE}
winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)
#saveRDS(winners,"cvData/complexOptimWins.rds")
```

@@

  source_python('src/dsurv.py')
  coxnnsurv=fitDeepSurv(train,fullTest,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv)
  coxnnsurv<-t(coxnnsurv)
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-times
  py_run_string("del fitDeepSurv")
  rm(fitDeepSurv)

@@

  print(paste("current iter:",pos))
  #saveRDS(BrierIPAList,'results/100complexBrier.rds')
  #saveRDS(cScore,'results/100complexcidx.rds')
  #saveRDS(AUClist,'results/100complexAuc.rds')
  pos=pos+1
  rm(train,val,fullTest)
}

@@

paramTrials<-as.data.frame(tidyr::crossing(lr=c(0.001,0.01,0.1),
                                           drpt=c(0.25),
                                           layer1=c(10,25,50,100),
                                           layer2=c(10,25,50,100),
                                           bsize=c(floor(nrow(klist[[1]]$train)/250)),
                                           actv=c("relu","tanh"),
                                           alp=c(0,0.5,1),
                                           k=c(3,6,9),
                                           dist=c('weibull','lognormal'),
                                           #IPA=NA,
                                           #IPAse=NA,
                                           valLoss=NA,
                                           runtime=NA))

@@

    lr=paramTrials[i,]$lr
    drpt=paramTrials[i,]$drpt
    layer1=paramTrials[i,]$layer1
    layer2=paramTrials[i,]$layer2
    bsize=paramTrials[i,]$bsize
    actv=paramTrials[i,]$actv
    alp=paramTrials[i,]$alp
    k=paramTrials[i,]$k
    dist=paramTrials[i,]$dist
    #=paramTrials[i,]$IPA
    #=paramTrials[i,]$valLoss

@@

  #paramTrials$IPA[i]<-mean(tempRes)
  #paramTrials$IPAse[i]<-sd(tempRes)
  paramTrials$valLoss[i]<-mean(tempVal)
  paramTrials$runtime[i]<-mean(runTime)
  print(paste("trial",i))
  print(mean(runTime))
  #print(as.character(paramTrials[i,]))
  #rm(cbnn,fit,annPreds,covars_input,covars_output)
  gc()
}

>>>>

res = split(data, g)
saveRDS(res$test,"cvData/ComplexSimTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
saveRDS(klist,"cvData/ComplexSimCV.rds")

@@

```{r,eval=TRUE,hide=FALSE}
winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)
saveRDS(winners,"cvData/complexOptimWins.rds")
```

@@

  source_python('src/dsurv.py')
  coxnnsurv=fitDeepSurv(train,fullTest,bsize,epochs=epo,valida=val,
                        patience=patience,min_delta=min_delta,drpt=drpt,
                        lay1=layer1,lay2=layer2,lr=lr,actv=actv)
  coxnnsurv<-t(coxnnsurv)
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-times
  py_run_string("del fitDeepSurv")
  rm(fitDeepSurv)

@@

  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100complexBrier.rds')
  saveRDS(cScore,'results/100complexcidx.rds')
  saveRDS(AUClist,'results/100complexAuc.rds')
  pos=pos+1
  rm(train,val,fullTest)
}

@@

paramTrials<-as.data.frame(tidyr::crossing(lr=c(0.001,0.01,0.1),
                                           drpt=c(0.25),
                                           layer1=c(10,25,50,100),
                                           layer2=c(10,25,50,100),
                                           bsize=c(floor(nrow(klist[[1]]$train)/250)),
                                           actv=c("relu","tanh"),
                                           alp=c(0,0.5,1),
                                           k=c(3,6,9),
                                           dist=c('weibull','lognormal'),

                                           valLoss=NA,
                                           runtime=NA))

@@

    lr=paramTrials[i,]$lr
    drpt=paramTrials[i,]$drpt
    layer1=paramTrials[i,]$layer1
    layer2=paramTrials[i,]$layer2
    bsize=paramTrials[i,]$bsize
    actv=paramTrials[i,]$actv
    alp=paramTrials[i,]$alp
    k=paramTrials[i,]$k
    dist=paramTrials[i,]$dist

@@

  paramTrials$valLoss[i]<-mean(tempVal)
  paramTrials$runtime[i]<-mean(runTime)
  print(paste("trial",i))
  print(mean(runTime))

  gc()
}
